A-maze of Natural Stories: Texts are comprehensible using the Maze task

### 2020-08-28 Papers/Amlap_2020_talk/amlap_2020_talk.tex
tweaks to talk

%TODO maybe put a picture of Roger's face??, at least acknowledge him 
\end{center}
\end{frame}

\begin{frame}{Incremental processing methods}
\pause
Want a measure of processing difficulty\pause

Assume that longer RT = more difficulty \pause
\smallskip
\begin{center}
{\large How to measure RT?}
\end{center}
\end{frame}
\begin{frame}{Incremental processing methods}

{\large Common ways to measure RT}
\begin{columns}[t]\pause
	\begin{column}{.5\textwidth}
		\begin{center}
			\textbf{\large Eye-tracking}

@@

Run items through LM, choose high surprisal words as distractors
\pause

Add some restrictions:
\begin{itemize}
\item Restrict to a list of possible distractors
\item Only consider length, frequency matches
\end{itemize}

\end{frame}
%
\begin{frame}{Does it work?} 
\pause
\vskip -2em
{\large Yes, at least well enough.} \pause
\begin{itemize}
	\item Sometimes generates plausible distractors. \pause
	\item A-maze results comparable with G-maze {\small(Boyce et al 2020, Sloggett et al 2020)} \pause 
\end{itemize} 
\medskip
\centering

@@

Problem: Errors terminate sentences. \pause
\begin{itemize}
	\item Treat whole story as a unit: \pause ~ No one makes it to the end. \pause
	\item Treat each sentence as a unit: \pause Some participants miss key context. \pause
\end{itemize}

@@

\end{frame}
%%So now that I've explained the method, going to switch over to current experiment & what we hoped to get from it
%
\begin{frame}{Current experiment}
	Various open questions to address \pause
	\begin{itemize}
		\item Are people willing to read long texts in this way? \pause
		\item Do people comprehend what they read? \pause
		\item Does the error correction variant work? \pause
		\item Do we get predictability effects? 
	\end{itemize}
\end{frame}

@@

Fit GAMs
\begin{itemize}
	\item Limit to single-token words
	\item Fit to both current and past word surprisal
	\item Include frequency, length as predictors
\end{itemize}

@@

\begin{frame}{Surprisal Effects}
	Linear Models \\
	\pause

@@

\end{frame}
\begin{frame}{Surprisal Effects}
	Takeaways: \pause
	\begin{itemize}
		\item Minimal frequency effects (consistent with Shain 2019) \pause
		\item Long RTs \pause
		\item Large effects of Length, Surprisal \pause
		\item Very little spillover \pause
	\end{itemize}

	Model comparison: GRNN is best, but TXL complementary
\end{frame}

\begin{frame}{Why such large effects?}
	\pause
	Framework: Look at words long enough to ID with some threshold of certainty \pause

Could hypothesize mechanisms for difference: \pause
\begin{itemize}
	\item Task leads to higher threshold \pause 
	\item Task demands reduce available resources for processing \pause
	\item Presence of second word 
\end{itemize}

@@

@@

>>>>

\end{center}
\end{frame}

%\begin{frame}{Incremental processing methods}
%\pause
%Want a measure of processing difficulty\pause
%
%Assume that longer RT = more difficulty \pause
%\smallskip
%\begin{center}
%{\large How to measure RT?}
%\end{center}
%\end{frame}
\begin{frame}{Incremental processing methods}
	\pause
{\large Common ways to measure RT}
\begin{columns}[t]\pause
	\begin{column}{.5\textwidth}
		\begin{center}
			\textbf{\large Eye-tracking}

@@

Run items through LM, choose high surprisal words as distractors

%Add some restrictions:
%\begin{itemize}
%\item Restrict to a list of possible distractors
%\item Only consider length, frequency matches
%\end{itemize}
%	
\end{frame}
%
\begin{frame}{Does it work?} 
\pause
\vskip -2em
{\large Yes, at least well enough.} \pause
\begin{itemize}
	\item Sometimes generates plausible distractors. \pause
	\item A-maze results comparable with G-maze {\small(Boyce et al 2020, Sloggett et al 2020)} \pause 
\end{itemize} 
\medskip
\centering

@@

Problem: Errors terminate sentences. \pause
\begin{itemize}
	\item Treat whole story as a unit: \pause Few participants make it to the end. \pause
	\item Treat each sentence as a unit: \pause Some participants miss key context. \pause
\end{itemize}

@@

\end{frame}
%%So now that I've explained the method, going to switch over to current experiment & what we hoped to get from it
%
\begin{frame}{Current experiment}
	Various open questions to address \pause
	\begin{itemize}
		\item Will people read long texts in Maze? \pause
		\item Will they comprehend what they read? \pause
		\item Does error correction Maze work? \pause
		\item Do we get predictability effects? 
	\end{itemize}
\end{frame}

@@

Fit GAMs
\begin{itemize}
	%\item Limit to single-token words
	\item Fit to both current and past word surprisal
	\item Include frequency, length as predictors
\end{itemize}

@@

\begin{frame}{Surprisal Effects}
	\vskip -2em
	Linear Models \\
	\pause

@@

\end{frame}
%\begin{frame}{Surprisal Effects}
%	Takeaways: \pause
%	\begin{itemize}
%		\item Minimal frequency effects (consistent with Shain 2019) \pause
%		\item Long RTs \pause
%		\item Large effects of Length, Surprisal \pause
%		\item Very little spillover \pause
%	\end{itemize}
%	
%	Model comparison: GRNN is best, but TXL complementary
%\end{frame}

\begin{frame}{Why such large effects?}
	\pause
	Bayesian reader framework: Look at words long enough to ID with some threshold of certainty \pause

Possible mechanisms for difference: \pause
\begin{itemize}
	\item Higher threshold \pause 
	\item Fewer available resources for processing \pause
	\item Presence of second word 
\end{itemize}

@@

\begin{frame}
	\centering
	\includegraphics[clip, trim=3.25cm 5cm 2.5cm 2.5cm,width=.9\textwidth]{../flow_2.pdf}
\end{frame}

\begin{frame}{Caveats}

	{\large Definitely some bad distractors}
	\begin{table}

		\begin{tabular}{rlll}
			Prefix & Correct & Distractor & Error Rate \\
			\hline
			\hline
			Gulordava&&&\\
			\hline
			The & niece & cooks & 44\%\\
			The swimmer & disappointed & propositions & 30\%\\
			The & semester & steroids & 29\%\\
			\hline
			\hline
			Jozefowicz&&&\\
			\hline
			The & husband & authors & 46\%\\
			Jim & listened & survived & 43\%\\
			The & uncle & roads & 42\%\\
			The & knight & saints & 40\%\\
		\end{tabular}
	\end{table}

@@

\begin{frame}{Links}

	\textcolor{ForestGreen}{\large Documentation: vboyce.github.io/Maze}

	with links to the following:
	\begin{itemize}

		\item A-maze code: github.com/vboyce/Maze

		\item Web-maze code: github.com/vboyce/Ibex-with-Maze

		\item Sample task: syntaxgym.org:666

		\item Paper: psyarxiv.com/b7nqd/
	\end{itemize}
\end{frame}

\begin{frame}{Matching distractors}
	If unspecified: Match by position
	\begin{itemize}
		\item The son of the lady who politely introduced \sethlcolor{green} \hl{herself}\sethlcolor{pink} / \hl{himself} was popular at the party.
	\end{itemize}
	Can specify labels for each word to pair (within item)
	\begin{itemize}
		\item The cat who the dog scared hid in a box.\\pre-1 pre-2 who art noun verb main-verb post-1 post-2 post-3
		\item The dog who scared the cat sniffed around the couch.\\ pre-1 pre-2 who verb art noun main-verb post-1 post-2 post-3
	\end{itemize}
\end{frame}
